---
title: "Category C Profit vs Utilization Report""  

date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    theme: flatly
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 1
    code_folding: show
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```


```{r libraries}
library(DT)
library(readxl)
library(tidyverse)
library(ggthemes)
library(ggrepel)
library(plotly)
library(extrafont)
library(DataExplorer)
library(tidyquant)
library(formattable)
library(glue)
library(paletteer)
library(prettydoc)
library(kableExtra)
```


This is a proof of concept report, which includes exploring three recreational programs from FY18 thru FY20. 

Recreation Programs are: 

  1. 5860 Golf Courses
  
  2. 5851 Private Berthing (Boat Slips)
  
  3. 5852 Boating Program (Rentals / Lessons)
  
Terms of Reference: 

  1. Active Duty Percent = Active Duty + Family Members / All Patrons
  
  2. Net Profit Percent = Net Profit / Net Sales


```{r}
# Utilization Data ----
Utilization <- read_excel(path = "/Users/barnesj/OneDrive - USMC-MCCS.ORG/Utilization/Utilization.xlsx", sheet = "Utilization", col_types = c("text", "text", "text", "text", "numeric"))
# Tidy and Prep for Joining Utilization Data

 Utl <- Utilization %>% 
    pivot_wider(names_from = Category, values_from = Utilization, values_fill = 0) %>% 
    rename_with(~ tolower(gsub("-", "_", .x, fixed = TRUE))) %>% 
    rename_with(~ tolower(gsub(",", "_", .x, fixed = TRUE))) %>% 
    rename_with(~ tolower(gsub(" ", "_", .x, fixed = TRUE))) %>% 
    rename_with(~ tolower(gsub("(", "_", .x, fixed = TRUE))) %>% 
    rename_with(~ tolower(gsub(")", "_", .x, fixed = TRUE))) %>% 
    rename_with(~ tolower(gsub("/", "_", .x, fixed = TRUE))) %>% 
    
    mutate(total_non_active = reserve + 
             retiree + dod_civilian + other_guest + 
             ret_e1_e5 + ret_e6_e9__o1_o3__w1_wo3 +
             ret_o4_o10__wo4_wo5 + dod_gs_1_6__nf_1_2 + dod_gs_7_11__nf_3_4 + 
             dod_gs_12_15__nf_5_6 + youth__8_18_ + guest + general_public  + 
             patron_expansion + tournament + pre_standard_pass_rounds + no_demographic_linked,
           total_active =  e1_e5  + e6_e9 + w1_w5 + o1_o3 + o4_o10 + w1_w3 + w4_w5 + family_member,
           total = total_active + total_non_active) %>% 
    
    select(cost_center, fy, company, total_active, total) %>% 
    rename("Cost_Center" = cost_center,
           "FY" = fy,
           "Company" = company) %>% 
    group_by(Cost_Center, Company) %>% 
    summarise(total_active = sum(total_active), 
             total = sum(total)) %>% 
    mutate(total_act_pct = total_active / total) %>% 
    mutate_all(~replace(., is.nan(.), 0))
 
 
 # Table Utilization (Keeps FY)
 
  utl_table <-  Utilization %>% 
    pivot_wider(names_from = Category, values_from = Utilization, values_fill = 0) %>% 
    rename_with(~ tolower(gsub("-", "_", .x, fixed = TRUE))) %>% 
    rename_with(~ tolower(gsub(",", "_", .x, fixed = TRUE))) %>% 
    rename_with(~ tolower(gsub(" ", "_", .x, fixed = TRUE))) %>% 
    rename_with(~ tolower(gsub("(", "_", .x, fixed = TRUE))) %>% 
    rename_with(~ tolower(gsub(")", "_", .x, fixed = TRUE))) %>% 
    rename_with(~ tolower(gsub("/", "_", .x, fixed = TRUE))) %>% 
    
    mutate(total_non_active = reserve + 
             retiree + dod_civilian + other_guest + 
             ret_e1_e5 + ret_e6_e9__o1_o3__w1_wo3 +
             ret_o4_o10__wo4_wo5 + dod_gs_1_6__nf_1_2 + dod_gs_7_11__nf_3_4 + 
             dod_gs_12_15__nf_5_6 + youth__8_18_ + guest + general_public  + 
             patron_expansion + tournament + pre_standard_pass_rounds + no_demographic_linked,
           total_active =  e1_e5  + e6_e9 + w1_w5 + o1_o3 + o4_o10 + w1_w3 + w4_w5 + family_member,
           total = total_active + total_non_active) %>% 
    
    select(cost_center, fy, company, total_active, total) %>% 
    rename("Cost_Center" = cost_center,
           "FY" = fy,
           "Company" = company)  %>% 
    group_by(FY, Cost_Center, Company) %>% 
    summarise(total_active = sum(total_active), 
             total = sum(total)) %>% 
    mutate(total_act_pct = total_active / total) %>% 
    mutate_all(~replace(., is.nan(.), 0))



```



```{r}
#Financial Data ----
# Load in Finacial extract data
extract <- read_excel(path = "/Users/barnesj/OneDrive - USMC-MCCS.ORG/Utilization/PL_fiveyear_extract_05282021.xlsx", sheet = "Extract")
#Select only the columns we need
extract <- extract %>% 
  select(Cost_Center, Cost_Center_Description, Cost_Center_Full, Company, Company_Description, ORG_Description, GL_Account_Description, `2020`, `2019`, `2018`, `2017`, `2016`)
# Only select the rows that contain Net Sales and Net Profit then save as profit
profit <- extract %>% 
  filter(GL_Account_Description %in% c("NET SALES", "NET PROFIT")) 

#Cat C Winners and Losers (2019 and 2020)
catc <- read_excel("/Users/barnesj/OneDrive - USMC-MCCS.ORG/Utilization/PL_fiveyear_extract_05282021.xlsx", sheet = "CatC")

#Load in total population data (Active, Retiree and Depn within 50 miles)
pop <- read_excel(path = "/Users/barnesj/OneDrive - USMC-MCCS.ORG/Utilization/Population_data.xlsx", sheet = "Population")

```

```{r scripts}
source("/Users/barnesj/OneDrive - USMC-MCCS.ORG/Utilization/functions/quad_plot.R")
source("/Users/barnesj/OneDrive - USMC-MCCS.ORG/Utilization/functions/catc_table.R")
```


```{r}
font <- list(
  size = 15,
  color = "white",
  fmaily = "Computer Modern"
)

label <- list(
  bgcolor = "2e3c50",
  bordercolor = "transparnet",
  font = font
)



```


## Data Dictionary

### Cost Center Descriptions 


```{r}

datatable(unique(profit[c("Cost_Center", "Cost_Center_Description")]))
```


### Company Abb & Desc 

```{r}

datatable(unique(profit[c("Company", "Company_Description")]))

```

## Plots and Tables 

### 5860 - Golf Courses Plot
Recreation Program

```{r}

golf <- quad_plot("5860 GOLF COURSE")

ggplotly(golf, tooltip = c("text"), height = 500, width = 900) %>% 
  layout( font = font)
  #config(displayModeBar = FALSE)

```
*Active duty includes Dependents


### 5860 - Golf Course Table 
The below table displays Percent Net Profit (FY18-FY20) and Percent use by Active duty (FY18-FY20) against all patrons that utilized the program. 

```{r}

table("5860 GOLF COURSE")

```

### 5851 - Private Berthing Plot
Recreation Program

```{r}

berthing <- quad_plot("5851 PRIVATE BERTHING")

ggplotly(berthing, tooltip = "text", height = 500, width = 900) %>% 
  layout( font = font) 
 #config(displayModeBar = FALSE)
```

*Active duty includes Dependents

### 5851 - Private Berthing Table 
The below table displays Percent Net Profit (FY18-FY20) and Percent use by Active duty (FY18-FY20)  against all patrons that utilized the program. 

```{r}

table("5851 PRIVATE BERTHING")

```

### 5852 - Boating Program Plot
Recreation Program

```{r}

boating <-quad_plot("5852 BOATING PROGRAM") 

 
ggplotly(boating, tooltip = c("text"), height = 500, width = 900) %>% 
  layout( font = font) 
  #config(displayModeBar = FALSE)


```

*Active duty includes Dependents


### 5852 - Boating Program Table 
The below table displays Percent Net Profit (FY18-FY20) and Percent use by Active duty (FY18-FY20) against all patrons that utilized the program. 

```{r}

table("5852 BOATING PROGRAM")

```

### 5853 - Vehicle Storage Plot
Recreation Program

```{r}
veh_stor <- quad_plot("5853 VEHICLE STORAGE")

 
ggplotly(veh_stor, tooltip = c("text"), height = 500, width = 900) %>% 
  layout( font = font) 
 #config(displayModeBar = FALSE)

```

*Active duty includes Dependents


### 5853 - Vehicle Storage Table
The below table displays Percent Net Profit (FY18-FY20) and Percent use by Active duty (FY18-FY20) members against all patrons that utilized the program. 

```{r}
table("5853 VEHICLE STORAGE")
```

### 5535 Auto Skills Plot
Recreation Program

```{r}
auto_skills <- quad_plot("5535 AUTO SKILLS")

 
ggplotly(auto_skills, tooltip = c("text"), height = 500, width = 900) %>% 
  layout( font = font) 
 #config(displayModeBar = FALSE)

```

*Active duty includes Dependents


### 5835 - Auto Skills Table
The below table displays Percent Net Profit (FY18-FY20) and Percent use by Active duty (FY18-FY20) against all patrons that utilized the program. 

```{r}
table("5535 AUTO SKILLS")
```

### 5811 / 5812 Bowling Plot
5811 - Bowling (16 lanes or less)  
5812 - Bowling (17 lanes or more)


```{r}

bowling <-  profit %>% 
    
    filter(!is.na(ORG_Description)) %>% 
  
    rename("FY20" = `2020`,
           "FY19" = `2019`,
           "FY18" = `2018`,
           "FY17" = `2017`,
           "FY16" = `2016`) %>%
    
    group_by(Cost_Center, Cost_Center_Description, Cost_Center_Full, Company, Company_Description, GL_Account_Description) %>% 
    summarise(sum = sum(FY20+ FY19 + FY18 + FY17 + FY16)) %>% 
    pivot_wider(names_from = GL_Account_Description, values_from = sum, values_fill = 0) %>% 
    ungroup() %>% 
    rename(Net_Sales = `NET SALES`,
           Net_Profit = `NET PROFIT`) %>%
    mutate_all(~replace(., is.nan(.), 0)) %>% 
    
    filter(Cost_Center_Full %in% c("5811 BOWLING (16 LANES OR LESS)", "5812 BOWLING (17 LANES OR MORE)")) %>% 
    inner_join(Utl, by = c("Cost_Center","Company")) %>% 
   
       group_by(Company, Company_Description) %>% 
       summarise(Net_Profit= sum(Net_Profit),
              Net_Sales = sum(Net_Sales),
              mean_act_pct = mean(total_act_pct)) %>% 
       mutate(pct = Net_Profit / Net_Sales)  %>% 
  
   
    ggplot(aes(mean_act_pct, pct, text = paste0("Company: ", Company,
                                                "\n Percent Active Duty: ", scales::percent(mean_act_pct),
                                                "\n Percent Net Profit: ", scales::percent(pct)), 
               color = Company)) + 
    geom_point() +
    geom_vline(aes(xintercept = .44)) +
    geom_hline(aes(yintercept = 0.0)) + 
    scale_y_continuous(labels = scales::percent) +
    scale_x_continuous(labels = scales::percent, limits = c(0, 1)) +
    labs( y = "Percent Net Profit (FY16-FY20)",
          x = "Percent use by Active Duty (FY18-FY20)*",
      caption = "*Active duty includes Dependents"
    ) + 
    theme_tq() + 
    theme(panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          strip.text =  element_text(
            face = "bold"),
          plot.caption = element_text(
            face = "bold")
    )
  

ggplotly(bowling, tooltip = c("text"), height = 500, width = 900) %>% 
  layout( font = font) 
 #config(displayModeBar = FALSE)

```
*data does not include Okinawa and SDM includes utilization data fro only (FY19 & FY20)

### 5811 / 5812 Bowling Table*  

The below table displays Percent Net Profit (FY18-FY20) and Percent use by Active duty (FY18-FY20) against all patrons that utilize both 5811 - Bowling (16 lanes or less) and/or 5812 - Bowling (17 lanes or more)

```{r}
  profit %>% 
    # Remove rows where Org description is missing
    filter(!is.na(ORG_Description)) %>% 
    # Cleanup column names
    rename("FY20" = `2020`,
           "FY19" = `2019`,
           "FY18" = `2018`,
           "FY17" = `2017`,
           "FY16" = `2016`) %>% 
    # Pivot FY column names to rows
    pivot_longer(!Cost_Center:GL_Account_Description, names_to = "FY", values_to = "Utilization") %>%
    # Group by then summaries total utilization 
    group_by(Cost_Center, Cost_Center_Description, Cost_Center_Full, Company, Company_Description, GL_Account_Description, FY) %>% 
    summarise(Total = sum(Utilization)) %>% 
    pivot_wider(names_from = GL_Account_Description, values_from = Total, values_fill = 0) %>% 
    ungroup() %>% 
    rename(Net_Sales = `NET SALES`,
           Net_Profit = `NET PROFIT`) %>%
    # add column for Net Profit Percent
    mutate(pct = Net_Profit/Net_Sales) %>% 
    # filter costs center you want to vicsualize
    filter(Cost_Center_Full %in% c("5811 BOWLING (16 LANES OR LESS)", "5812 BOWLING (17 LANES OR MORE)")) %>% 
    # Join Marinas data using Company and FY
    inner_join(utl_table, by = c("Cost_Center", "Company", "FY")) %>%
    # Join the population data
    select(FY,Cost_Center, Company_Description, Cost_Center_Description, pct, total_act_pct) %>% 
    rename(
      "Cost Cener" = Cost_Center, 
      "Cost Center Desc" = Cost_Center_Description,
      "Company Desc" = Company_Description, 
      #"FY" = FY.x, 
      # "Net Profit" = Net_Profit,
      # "Net Sales" = Net_Sales,
      "Percent Net Profit" = pct, 
      # "Active Duty Patron" = total_active, 
      # "Total Non Active Patron" = total_non_active, 
      # "Total Patrons" = Total, 
      "Percent use by Active Duty" = total_act_pct
      # "Active Pop" = activepop, 
      # "Retiree Pop" = retirepop,
      # "Depn Pop" = deppop,
      # "Total Eligable Pop" = total_pop
    ) %>% 
    mutate(`Percent Net Profit` = scales::percent(`Percent Net Profit`),
           `Percent use by Active Duty` = scales::percent(`Percent use by Active Duty`)) %>% 
    datatable(rownames = FALSE, extensions = 'RowGroup',
              options = list(rowGroup = list(dataSrc = 3,
                             columnDefs = list(list(className = 'dt-center', targets = 0:5), 
                                              list(targets = 5, visible = TRUE) 
                                              ),
                             pageLength = 10, autowidth = FALSE),
              selection = 'none'
              # caption = htmltools::tags$caption(
              #   style = 'caption-side: top; text-align: left;',
              #   'Table 1: ', htmltools::em('Program Grouped by Installation.')
    )) %>% 
    formatStyle(columns = "Percent Net Profit", color = styleInterval(0, c("red", "black")))
                
```
*Utilization metrics are combined for both 5811 and 5812.  
If Net Profit is blank, there is no bowling (< 16 or > 17 Lanes) program for that installation.  
RecTrac (Utilization) data was not collected for San Diego until FY19

### 5572 / 5573 / 5575 - ITT Ticket / ITT Tours / Direct Leisure Travel Plot

```{r}

ITT <- profit %>% 
    
    filter(!is.na(ORG_Description)) %>% 
  
    rename("FY20" = `2020`,
           "FY19" = `2019`,
           "FY18" = `2018`,
           "FY17" = `2017`,
           "FY16" = `2016`) %>%
    
    group_by(Cost_Center, Cost_Center_Description, Cost_Center_Full, Company, Company_Description, GL_Account_Description) %>% 
    summarise(sum = sum(FY20+ FY19 + FY18 + FY17 + FY16)) %>% 
    pivot_wider(names_from = GL_Account_Description, values_from = sum, values_fill = 0) %>% 
    ungroup() %>% 
    rename(Net_Sales = `NET SALES`,
           Net_Profit = `NET PROFIT`) %>%
    mutate_all(~replace(., is.nan(.), 0)) %>% 
    
    filter(Cost_Center_Full %in% c("5575 DIRECT LEISURE TRAVEL", "5572 ITT TICKET", "5573 ITT TOURS" )) %>%
    inner_join(Utl, by = c("Cost_Center","Company")) %>% 
   
       group_by(Company, Company_Description) %>% 
       summarise(Net_Profit= sum(Net_Profit),
              Net_Sales = sum(Net_Sales),
              mean_act_pct = mean(total_act_pct)) %>% 
       mutate(pct = Net_Profit / Net_Sales) %>% 


    ggplot(aes(mean_act_pct, pct, text = paste0("Company: ", Company,
                                                "\n Percent Active Duty: ", scales::percent(mean_act_pct),
                                                "\n Percent Net Profit: ", scales::percent(pct)), 
               color = Company)) + 
    geom_point() +
    geom_vline(aes(xintercept = mean(mean_act_pct))) +
    geom_hline(aes(yintercept = 0.0)) + 
    scale_y_continuous(labels = scales::percent) +
    scale_x_continuous(labels = scales::percent, limits = c(0, 1)) +
    labs( y = "Percent Net Profit (Avg FY16-FY20)",
          x = "Percent use by Active Duty (Avg FY18-FY20)*",
      caption = "*Active duty includes Dependents"
    ) + 
    theme_tq() + 
    theme(panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          strip.text =  element_text(
            face = "bold"),
          plot.caption = element_text(
            face = "bold")
    )
  

ggplotly(ITT, tooltip = c("text"), height = 500, width = 900) %>% 
  layout( font = font) 
 #config(displayModeBar = FALSE)
```

### 5572 / 5573 / 5575 - ITT Ticket / ITT Tours / Direct Leisure Travel Table*  

The below table displays Percent Net Profit (FY18-FY20) and Percent use by Active duty (FY18-FY20) against all patrons that utilize  
5572 - ITT Ticket, 5573 - ITT Tours and 5575 Direct Leisure Travel 

```{r}
profit %>% 
    # Remove rows where Org description is missing
    filter(!is.na(ORG_Description)) %>% 
    # Cleanup column names
    rename("FY20" = `2020`,
           "FY19" = `2019`,
           "FY18" = `2018`,
           "FY17" = `2017`,
           "FY16" = `2016`) %>% 
    # Pivot FY column names to rows
    pivot_longer(!Cost_Center:GL_Account_Description, names_to = "FY", values_to = "Utilization") %>%
    # Group by then summaries total utilization 
    group_by(Cost_Center, Cost_Center_Description, Cost_Center_Full, Company, Company_Description, GL_Account_Description, FY) %>% 
    summarise(Total = sum(Utilization)) %>% 
    pivot_wider(names_from = GL_Account_Description, values_from = Total, values_fill = 0) %>% 
    ungroup() %>% 
    rename(Net_Sales = `NET SALES`,
           Net_Profit = `NET PROFIT`) %>%
    # add column for Net Profit Percent
   
    # filter costs center you want to vicsualize
    filter(Cost_Center_Full %in% c("5575 DIRECT LEISURE TRAVEL", "5572 ITT TICKET", "5573 ITT TOURS" )) %>% 
    # Join Marinas data using Company and FY
    inner_join(utl_table, by = c("Cost_Center", "Company", "FY")) %>% 
    group_by(Company, Company_Description, FY) %>% 
    summarise(Net_Profit = sum(Net_Profit),
              Net_sales = sum(Net_Sales), 
              total_actice = sum(total_active),
              total = sum(total), 
              total_act_pct = mean(total_act_pct)) %>% 
    mutate(pct = Net_Profit/Net_sales) %>% 
    # Join the population data
    select(FY, Company_Description, pct, total_act_pct) %>% 
    rename(
      # "Cost Cener" = Cost_Center, 
      # "Cost Center Desc" = Cost_Center_Description,
      "Company Desc" = Company_Description, 
      #"FY" = FY.x, 
      # "Net Profit" = Net_Profit,
      # "Net Sales" = Net_Sales,
      "Percent Net Profit" = pct, 
      # "Active Duty Patron" = total_active, 
      # "Total Non Active Patron" = total_non_active, 
      # "Total Patrons" = Total, 
      "Percent use by Active Duty" = total_act_pct
      # "Active Pop" = activepop, 
      # "Retiree Pop" = retirepop,
      # "Depn Pop" = deppop,
      # "Total Eligable Pop" = total_pop
    ) %>% 
    mutate(`Percent Net Profit` = scales::percent(`Percent Net Profit`),
           `Percent use by Active Duty` = scales::percent(`Percent use by Active Duty`)) %>% 
    datatable(rownames = FALSE, extensions = 'RowGroup',
              options = list(rowGroup = list(dataSrc = 0),
                             columnDefs = list(list(className = 'dt-center', targets = 1:4), 
                                              list(targets = 4, visible = FALSE) 
                                              ),
                             pageLength = 10, autowidth = TRUE),
              selection = 'none'
              # caption = htmltools::tags$caption(
              #   style = 'caption-side: top; text-align: left;',
              #   'Table 1: ', htmltools::em('Program Grouped by Installation.')
    ) %>% 
    formatStyle(columns = "Percent Net Profit", color = styleInterval(0, c("red", "black")))
```
*Table combines CCTR's 5575, 5572 and 5573 as one program (Net Profit and Utilization)


```{r}
knitr::knit_exit()
```

#### Sandbox Code

Utilization for quad plot (Summarises each FY by mean_act_pct)

```{r}
Utl <- Utilization %>% 
  pivot_wider(names_from = Category, values_from = Utilization, values_fill = 0) %>% 
  rename_with(~ tolower(gsub("-", "_", .x, fixed = TRUE))) %>% 
  rename_with(~ tolower(gsub(",", "_", .x, fixed = TRUE))) %>% 
  rename_with(~ tolower(gsub(" ", "_", .x, fixed = TRUE))) %>% 
  rename_with(~ tolower(gsub("(", "_", .x, fixed = TRUE))) %>% 
  rename_with(~ tolower(gsub(")", "_", .x, fixed = TRUE))) %>% 
  rename_with(~ tolower(gsub("/", "_", .x, fixed = TRUE))) %>% 
  
  mutate(total_non_active = reserve + 
           retiree + dod_civilian + other_guest + 
           ret_e1_e5 + ret_e6_e9__o1_o3__w1_wo3 +
           ret_o4_o10__wo4_wo5 + dod_gs_1_6__nf_1_2 + dod_gs_7_11__nf_3_4 + 
           dod_gs_12_15__nf_5_6 + youth__8_18_ + guest + general_public  + 
           patron_expansion + tournament + pre_standard_pass_rounds,
         total_active =  e1_e5  + e6_e9 + w1_w5 + o1_o3 + o4_o10 + w1_w3 + w4_w5 + family_member,
         total_act_pct = total_active / (total_active +total_non_active),
         total = total_active + total_non_active) %>% 
  
  select(cost_center, fy, company, total_act_pct) %>% 
  rename("Cost_Center" = cost_center,
         "FY" = fy,
         "Company" = company) %>% 
  group_by(Cost_Center, Company) %>% 
  summarise(mean_act_pct = mean(total_act_pct)) %>% 
  mutate_all(~replace(., is.nan(.), 0))

```

Utilization for Table (maintains each FY)

```{r}
 utl_table <- Utilization %>% 
    pivot_wider(names_from = Category, values_from = Utilization, values_fill = 0) %>% 
    rename_with(~ tolower(gsub("-", "_", .x, fixed = TRUE))) %>% 
    rename_with(~ tolower(gsub(",", "_", .x, fixed = TRUE))) %>% 
    rename_with(~ tolower(gsub(" ", "_", .x, fixed = TRUE))) %>% 
    rename_with(~ tolower(gsub("(", "_", .x, fixed = TRUE))) %>% 
    rename_with(~ tolower(gsub(")", "_", .x, fixed = TRUE))) %>% 
    rename_with(~ tolower(gsub("/", "_", .x, fixed = TRUE))) %>% 
    
    mutate(total_non_active = reserve + 
             retiree + dod_civilian + other_guest + 
             ret_e1_e5 + ret_e6_e9__o1_o3__w1_wo3 +
             ret_o4_o10__wo4_wo5 + dod_gs_1_6__nf_1_2 + dod_gs_7_11__nf_3_4 + 
             dod_gs_12_15__nf_5_6 + youth__8_18_ + guest + general_public  + 
             patron_expansion + tournament + pre_standard_pass_rounds,
           total_active =  e1_e5  + e6_e9 + w1_w5 + o1_o3 + o4_o10 + w1_w3 + w4_w5 + family_member,
           total_act_pct = total_active / (total_active +total_non_active),
           total = total_active + total_non_active) %>% 
    
    select(cost_center, fy, company, total_act_pct) %>% 
    rename("Cost_Center" = cost_center,
           "FY" = fy,
           "Company" = company) %>% 
    mutate_all(~replace(., is.nan(.), 0))

```

Quad_plot code for the Avg Net Profit Percent over the last five years (FY16 - FY20)

```{r}

  profit %>% 
    
    filter(!is.na(ORG_Description)) %>% 
  
    rename("FY20" = `2020`,
           "FY19" = `2019`,
           "FY18" = `2018`,
           "FY17" = `2017`,
           "FY16" = `2016`) %>%
    
    group_by(Cost_Center, Cost_Center_Description, Cost_Center_Full, Company, Company_Description, GL_Account_Description) %>% 
    summarise(average = sum(FY20+ FY19 + FY18 + FY17 + FY16)/(ncol(profit)-7)) %>% 
    pivot_wider(names_from = GL_Account_Description, values_from = average, values_fill = 0) %>% 
    ungroup() %>% 
    rename(Net_Sales = `NET SALES`,
           Net_Profit = `NET PROFIT`) %>%
  
    mutate(pct = Net_Profit/Net_Sales) %>%
    
    filter(Cost_Center_Full %in% c("5811 BOWLING (16 LANES OR LESS)", "5812 BOWLING (17 LANES OR MORE)" )) %>% 
   
    inner_join(Utl, by = c("Cost_Center", "Company")) %>%
    filter(Net_Profit != 0) %>% 
    group_by(Company, Company_Description) %>% 
    summarise(Net_Profit= mean(Net_Profit),
              Net_Sales = mean(Net_Sales), 
              pct = mean(pct), 
              mean_act_pct = mean(mean_act_pct)) %>% 
  
   
    ggplot(aes(mean_act_pct, pct, text = paste0("Company: ", Company,
                                                "\n Percent Active Duty: ", scales::percent(mean_act_pct),
                                                "\n Percent Net Profit: ", scales::percent(pct)), 
               color = Company)) + 
    geom_point() +
    geom_vline(aes(xintercept = .44)) +
    geom_hline(aes(yintercept = 0.0)) + 
    scale_y_continuous(labels = scales::percent) +
    scale_x_continuous(labels = scales::percent, limits = c(0, 1)) +
    labs( y = "Percent Net Profit (Avg FY16-FY20)",
          x = "Percent use by Active Duty (Avg FY18-FY20)*",
      caption = "*Active duty includes Dependents"
    ) + 
    theme_tq() + 
    theme(panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          strip.text =  element_text(
            face = "bold"),
          plot.caption = element_text(
            face = "bold")
    )
  
```

Code for the data table
```{r}
  profit %>% 
    # Remove rows where Org description is missing
    filter(!is.na(ORG_Description)) %>% 
    # Cleanup column names
    rename("FY20" = `2020`,
           "FY19" = `2019`,
           "FY18" = `2018`,
           "FY17" = `2017`,
           "FY16" = `2016`) %>% 
    # Pivot FY column names to rows
    pivot_longer(!Cost_Center:GL_Account_Description, names_to = "FY", values_to = "Utilization") %>%
    # Group by then summaries total utilization 
    group_by(Cost_Center, Cost_Center_Description, Cost_Center_Full, Company, Company_Description, GL_Account_Description, FY) %>% 
    summarise(Total = sum(Utilization)) %>% 
    pivot_wider(names_from = GL_Account_Description, values_from = Total, values_fill = 0) %>% 
    ungroup() %>% 
    rename(Net_Sales = `NET SALES`,
           Net_Profit = `NET PROFIT`) %>%
    # add column for Net Profit Percent
    mutate(pct = Net_Profit/Net_Sales) %>% 
    # filter costs center you want to vicsualize
     filter(Cost_Center_Full %in% c("5811 BOWLING (16 LANES OR LESS)", "5812 BOWLING (17 LANES OR MORE)" )) %>% 
    # Join Marinas data using Company and FY
    inner_join(utl_table, by = c("Cost_Center", "Company", "FY")) %>%
    # Join the population data
    inner_join(pop, by = "Company") %>% 
    select(FY,Cost_Center, Company_Description, Cost_Center_Description, pct, total_act_pct) %>% 
    rename(
      "Cost Cener" = Cost_Center, 
      "Cost Center Desc" = Cost_Center_Description,
      "Company Desc" = Company_Description, 
      "FY" = FY, 
      # "Net Profit" = Net_Profit,
      # "Net Sales" = Net_Sales,
      "Percent Net Profit" = pct, 
      # "Active Duty Patron" = total_active, 
      # "Total Non Active Patron" = total_non_active, 
      # "Total Patrons" = Total, 
      "Percent use by Active Duty" = total_act_pct
      # "Active Pop" = activepop, 
      # "Retiree Pop" = retirepop,
      # "Depn Pop" = deppop,
      # "Total Eligable Pop" = total_pop
    ) %>% 
    mutate(`Percent Net Profit` = scales::percent(`Percent Net Profit`),
           `Percent use by Active Duty` = scales::percent(`Percent use by Active Duty`)) %>% 
    datatable(rownames = FALSE, extensions = 'RowGroup',
              options = list(rowGroup = list(dataSrc = 3,
                                             buttons = 
                                               list(
                                                 "copy",
                                                 "print",
                                                 list(extend = "collection", 
                                                      buttons = c("csv", "excel", "pdf"),
                                                      text = "download")
                                               )),
                             pageLength = 10, autowidth = TRUE),
              selection = 'none'
              # caption = htmltools::tags$caption(
              #   style = 'caption-side: top; text-align: left;',
              #   'Table 1: ', htmltools::em('Program Grouped by Installation.')
    ) %>% 
    formatStyle(columns = "Percent Net Profit", color = styleInterval(0, c("red", "black")))
```



# Quad_plot Net Profit Percent over the last five years (FY16-FY20)

```{r}
 profit %>% 
    
    filter(!is.na(ORG_Description)) %>% 
  
    rename("FY20" = `2020`,
           "FY19" = `2019`,
           "FY18" = `2018`,
           "FY17" = `2017`,
           "FY16" = `2016`) %>%
    
    group_by(Cost_Center, Cost_Center_Description, Cost_Center_Full, Company, Company_Description, GL_Account_Description) %>% 
    summarise(sum = sum(FY20+ FY19 + FY18 + FY17 + FY16)) %>% 
    pivot_wider(names_from = GL_Account_Description, values_from = sum, values_fill = 0) %>% 
    ungroup() %>% 
    rename(Net_Sales = `NET SALES`,
           Net_Profit = `NET PROFIT`) %>%
    mutate_all(~replace(., is.nan(.), 0)) %>% 
    
    filter(Cost_Center_Full %in% c("5811 BOWLING (16 LANES OR LESS)", "5812 BOWLING (17 LANES OR MORE)")) %>%
    inner_join(Utl, by = c("Cost_Center","Company")) %>% 
   
       group_by(Company, Company_Description) %>% 
       summarise(Net_Profit= sum(Net_Profit),
              Net_Sales = sum(Net_Sales),
              mean_act_pct = mean(mean_act_pct)) %>% 
       mutate(pct = Net_Profit / Net_Sales) %>% 


    ggplot(aes(mean_act_pct, pct, text = paste0("Company: ", Company,
                                                "\n Percent Active Duty: ", scales::percent(mean_act_pct),
                                                "\n Percent Net Profit: ", scales::percent(pct)), 
               color = Company)) + 
    geom_point() +
    geom_vline(aes(xintercept = mean(mean_act_pct))) +
    geom_hline(aes(yintercept = 0.0)) + 
    scale_y_continuous(labels = scales::percent) +
    scale_x_continuous(labels = scales::percent, limits = c(0, 1)) +
    labs( y = "Percent Net Profit (Avg FY16-FY20)",
          x = "Percent use by Active Duty (Avg FY18-FY20)*",
      caption = "*Active duty includes Dependents"
    ) + 
    theme_tq() + 
    theme(panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          strip.text =  element_text(
            face = "bold"),
          plot.caption = element_text(
            face = "bold")
    )
```


