---
title: "Official Lodging Facilities" 

output:
  html_document:
    theme: flatly
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 2
    code_folding: none
params:
  date: "Sep 28, 2021"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, 
                      warning = FALSE, 
                      cache = TRUE, 
                      echo = FALSE,
                      fig.width = 10, 
                      fig.height=5)

unlink('Lodging_cache', recursive = TRUE)
```

```{css headings, echo=FALSE}

h1 {
  font-weight: bold;
  font-size: 28px;
  text-align: center;
}

h2 {
  font-weight: bold;
  font-size: 22px;
    text-align: center;
}

h3 {
  font-weight: bold;
  font-size: 24px;
}

h4 {
  font-weight: bold;
  font-size: 20px;
}

h5 {
  font-weight: bold;
  font-size: 16px;
}

```

```{r load-lib}
library(tidyverse)
library(ggthemes)
library(readxl)
library(DT)
library(gt)
library(tidyquant)
library(markdown)
library(writexl)

```

```{r read-data}

# Read in cat codes xlsx data and save data as RDS

cat_code <- read_xlsx(path = "/Users/barnesj/OneDrive - USMC-MCCS.ORG/Documents/Data/Github_data/MCCS_Facility_Inventory_Report.XLSX",
    sheet = "Cat_code",
    col_types = c("numeric", "text", "text", "text"
                  )
)

# Read in facility xlsx data and save data as RDS

fac <-  read_xlsx(path = "/Users/barnesj/OneDrive - USMC-MCCS.ORG/Documents/Data/Github_data/MCCS Facility Inventory Report - 2021-09-28_14-56-08.XLSX",
    sheet = "Facility",
    skip = 1,
    col_types = c(
      "text", "text", "text",
      "text", "text", "numeric",
      "numeric", "text", "numeric", "date", "date"
    )
  )


# Read in utilization xlsx data and save data as RDS
utl <-  read_xlsx("/Users/barnesj/OneDrive - USMC-MCCS.ORG/Documents/Data/Github_data/MCCS Facility Inventory Report - 2021-09-28_14-56-08.XLSX",
    sheet = "Utilization",
    skip = 1
  )


```

```{r wrangle}

# Clean Facility Data
fac_lodging <- fac %>%
  janitor::clean_names() %>%
  separate(mccs_installation_name, c("num", "installation"), sep = 7) %>%
  select(
    RPUID = i_nfads_real_property_unique_id,
    installation,
    prv = i_nfads_current_prv,
    fci = i_nfads_facility_condition_index,
    fci_dt = i_nfads_fci_date,
    infads_area = i_nfads_area,
    build_dt = i_nfads_facility_built_date
    
  ) %>%
  # coverting dates to ymd format
  mutate(
    # usecode = usecode %>% as.numeric(),
    fci_dt = ymd(fci_dt) %>% replace_na(ymd(0000 / 00 / 00)),
    infads_area = infads_area %>% replace_na(0),
    build_dt = ymd(build_dt) %>% replace_na(ymd(0000 / 00 / 00))
  ) %>%
  # adding new column called Q-Rating based on the FCI
  mutate(q_rating = case_when(
    fci <= 59 ~ "Q4",
    fci <= 79 ~ "Q3",
    fci <= 89 ~ "Q2",
    TRUE ~ "Q1"
  )) %>%
  # shorten installation (location) names
  mutate(installation = case_when(
    installation %>% str_to_lower() %>% str_detect("butler") ~ "MCB Butler",
    installation %>% str_to_lower() %>% str_detect("mcb camp pendleton") ~ "MCB Pendleton",
    installation %>% str_to_lower() %>% str_detect("mcb camp lejeune") ~ "MCB Lejeune",
    installation %>% str_to_lower() %>% str_detect("mcb hawaii") ~ "MCB Hawaii",
    installation %>% str_to_lower() %>% str_detect("mcas iwakuni") ~ "MCAS Iwakuni",
    installation %>% str_to_lower() %>% str_detect("mcas cherry") ~ "MCAS Cherry Point",
    installation %>% str_to_lower() %>% str_detect("marine corps base quantico") ~ "MCB Quantico",
    installation %>% str_to_lower() %>% str_detect("mcagcc") ~ "MCAGCC 29 Palms",
    installation %>% str_to_lower() %>% str_detect("miramar") ~ "MCAS Miramar",
    installation %>% str_to_lower() %>% str_detect("yuma") ~ "MCAS Yuma",
    installation %>% str_to_lower() %>% str_detect("san diego") ~ "MCRD San Diego",
    installation %>% str_to_lower() %>% str_detect("mcrd beaufort") ~ "MCRD PI",
    installation %>% str_to_lower() %>% str_detect("new river") ~ "MCAS New River",
    installation %>% str_to_lower() %>% str_detect("futenma") ~ "MCAS Futenma",
    installation %>% str_to_lower() %>% str_detect("mcas beaufort") ~ "MCAS Beaufort",
    installation %>% str_to_lower() %>% str_detect("barstow") ~ "MCLB Barstow",
    installation %>% str_to_lower() %>% str_detect("albany") ~ "MCLB Albany",
    installation %>% str_to_lower() %>% str_detect("orleans") ~ "MARFORRES",
    installation %>% str_to_lower() %>% str_detect("washington") ~ "MBW (8th & I)",
    installation %>% str_to_lower() %>% str_detect("garden") ~ "Garden City",
    installation %>% str_to_lower() %>% str_detect("bridgeport") ~ "MWTC Bridgeport",
    installation %>% str_to_lower() %>% str_detect("mujuk") ~ "Camp Mujuk",
    installation %>% str_to_lower() %>% str_detect("mcas camp pendleton") ~ "MCAS Pendleton",
    installation %>% str_to_lower() %>% str_detect("allen") ~ "Camp Elmore",
    installation %>% str_to_lower() %>% str_detect("mcsf") ~ "MCSF Blount Island",
    installation %>% str_to_lower() %>% str_detect("4th mardiv") ~ "HQ 4th MARDIV",
    installation %>% str_to_lower() %>% str_detect("mcsptact") ~ "Kansas City"
  )) %>%
  mutate(RPUID = RPUID %>% as.character()) %>%
 # create a Restoration and Modernization Column
  mutate(RM = prv * 0.025)

# Clean utilization data
utl_lodging <- utl %>%
  janitor::clean_names() %>%
  janitor::remove_empty(c("rows"), quiet = TRUE) %>%
  select(
    RPUID = i_nfads_real_property_unique_id,
    use = i_nfads_use_category_code,
    fac_num = i_nfads_facility_number,
    installation = mccs_installation_name,
    program = mccs_business_program,
    asset_name = i_nfads_real_property_asset_name,
    fac_use = i_nfads_facility_use,
    FY2022 = fsm_fy22_sustainment_cost,
    Cat = i_nfads_naf_category,
    adq = i_nfads_adq_area_measure,
    sub = i_nfads_sub_area_measure,
    iadq = i_nfads_iadq_area_measure,
    adq_alt = i_nfads_adq_alternate_measure,
    sub_alt = i_nfads_sub_alternate_measure,
    iadq_alt = i_nfads_iadq_alternate_measure,
    adq_other = i_nfads_adq_other_measure,
    sub_other = i_nfads_sub_other_measure,
    iadq_other = i_nfads_iadq_other_measure,
    other_unit_measure = i_nfads_other_unit_meas
  ) %>%
  #isolate use Category code in own column called "usecode"
  separate(use, into = c("use_code", "use_desc"), sep = 6) %>%
  mutate(use_code = use_code %>% as.numeric()) %>%
  # Remove bilieting not being absorbed by MCCS
  filter(RPUID %in% c(
    47876, 54005, 42721, 42722, 42728,20961,55067, 1402894,624330,31834,1276281,1168519,1171866,55442,985794,985798,33862,33863
,33864,33866,33867,33868,52828,44509,1418193,39447,1173406,1010443,921138,24975,25335,25336,24976,24977,1102653,18774,14521,547842
,38897,38886,38888,38887,38901,22706,36823,36814,46880,167081,27560,1289900, 27588,46193,51883,51233, 18650,42696
,42695,40527,52004,53326,40533,40523,40525,40531,20073,20590,54396,38687,548411,54004,43715,21578,33314,35077,35078,26800
)
) %>%
  # handling missing data
  mutate(
    adq = adq %>% replace_na(0),
    sub = sub %>% replace_na(0),
    iadq = iadq %>% replace_na(0),
    adq_other = adq_other %>% replace_na(0),
    sub_other = sub_other %>% replace_na(0),
    iadq_other = iadq_other %>% replace_na(0),
    adq_alt = adq_alt %>% replace_na(0),
    sub_alt = sub_alt %>% replace_na(0),
    iadq_alt = iadq_alt %>% replace_na(0),
    FY2022 = FY2022 %>% replace_na(0),
    use_code = if_else(RPUID == 1173406, 74020, use_code)
  ) %>%
  # create total columns for each type measure
  mutate(
    total_measure = adq + sub + iadq,
    alt_total_measure = adq_alt + sub_alt + iadq_alt,
    other_total_measure = adq_other + sub_other + iadq_other
  ) %>%
  mutate(region = case_when(
    installation %in% c(
      "M00146 MCAS CHERRY POINT NC",
      "M00263 MCRD BEAUFORT PI SC",
      "M60169 MCAS BEAUFORT SC",
      "M62573 MCAS NEW RIVER JAX NC",
      "M67001 MCB CAMP LEJEUNE NC",
      "M67004 MCLB ALBANY GA",
      "M67695 MCSF BLOUNT ISLAND"
    ) ~ "MCIEAST",
    installation %in% c(
      "M00264 MARINE CORPS BASE QUANTICO VA",
      "M67029 MARBKS WASHINGTON DC"
    ) ~ "MCINCR",
    installation %in% c(
      "M00318 MCB HAWAII KANEOHE",
      "M20810 CAMP MUJUK REPUBLIC OF KOREA",
      "M63026 MCAS FUTENMA JA",
      "M67400 MCB CAMP S D BUTLER OKINAWA JA",
      "M62613 MCAS IWAKUNI JA"
    ) ~ "MCIPAC",
    installation %in% c(
      "M00681 MCB CAMP PENDLETON CA",
      "M62204 MCLB BARSTOW CA",
      "M62974 MCAS YUMA AZ",
      "M67604 MCAS CAMP PENDLETON CA",
      "M67865 MCAS MIRAMAR"
    ) ~ "MCIWEST",
    installation %in% c(
      "M00243 MARCORPRCUITDEP SAN DIEGO CA",
      "M64495 MARCORPSMWTC BRIDGEPORT CA",
      "M67399 MCAGCC TWENTYNINE PALMS CA"
    ) ~ "SLTI",
    installation %in% c(
      "M09036 CAMP ALLEN",
      "M67011 MARCORPS DIST 1 GARDEN CITY NY",
      "M67386 MCSPTACT KANSAS CITY MO",
      "M67861 MARCORRESFOR NEW ORLEANS LA",
      "M68479 HDQTRS 4TH MARDIV NEW ORLEANS"
    ) ~ "NONE"
  )) %>%
  mutate(RPUID = RPUID %>% as.character())

fac_mapped_lodging <- utl_lodging %>%
  inner_join(cat_code, by = c("use_code" = "use_code"))

fac_mapped_lodging <- fac_mapped_lodging  %>%
  left_join(fac_lodging, by = c("RPUID")) %>% 
  filter(naf_cat %in% c("L", "L (TDY)", "L (PCS)")) 

df_clean_lodging <- fac_mapped_lodging %>%
 mutate(
    sus =  FY2022,
    sus = sus %>% replace_na(0)
  ) %>%
  # finding percentages if the facility area is blank on raw facility data
  
  # facility_area-measure = if_else(if facility area is > 0 then use facility areas otherwise 
  # if total_measure > 0 use total_measure otherwise
  # if alt_total_measure > use alt_total_measure otherwise
  # use other_total_measure
  mutate(
    # facility_area-measure = if_else(if facility area is > 0 then use facility areas otherwise 
    # if total_measure > 0 use total_measure otherwise
    # if alt_total_measure > use alt_total_measure otherwise
    # use other_total_measure
    fac_area_measure = if_else(infads_area > 0, infads_area,
                               if_else(total_measure > 0, total_measure,
                                       if_else(alt_total_measure > 0, alt_total_measure,
                                                other_total_measure))
    )) %>%
  group_by(RPUID) %>% 
  mutate(count = n()) %>% 
  ungroup() %>% 
  mutate(
    use_pct_area = if_else(total_measure > 0, total_measure / fac_area_measure, 1)) %>% 
                           
                           # if_else(alt_total_measure > 0, alt_total_measure / fac_area_measure,
                           #         if_else(other_total_measure > 0, other_total_measure / fac_area_measure, 1)))) %>% 
    
  mutate(
    use_pct_area = use_pct_area %>% replace_na(0)
  ) %>%
  mutate(
    RM_corrected = RM * use_pct_area,
    RM_corrected = RM_corrected %>% replace_na(0),
    use_pct_text = use_pct_area %>% scales::percent(),
    RM_corrected_text = RM_corrected %>% scales::dollar()
  )

# Create Final dataframe

df_lodging <- df_clean_lodging %>%
  select(region, installation = installation.y, RPUID, use_code, use_desc, fac_use, naf_cat, op_activity, fac_num, facility_desc, asset_name, fci, fci_dt, build_dt, 
         q_rating, total_measure, alt_total_measure, other_total_measure, other_unit_measure, fac_area_measure, prv,sus, RM, use_pct_area, RM_corrected)



```

```{r output}

# creates a xlsx output file of the cleaned data and stores in output folder
write_xlsx(df_lodging, "/Users/barnesj/OneDrive - USMC-MCCS.ORG/Documents/Data/Github_data/output/df_final_lodging.xlsx")
         
saveRDS(df_lodging, "/Users/barnesj/OneDrive - USMC-MCCS.ORG/Documents/Data/Github_data/output/df_final_lodging.rds")

```



<br>

<center>

Note: The current report is based on utilization information unless otherwise noted. 

Raw data pulled from GoRPM on `r params$date`

References:

Download raw Lodging data: [here](https://mccsorg-my.sharepoint.com/:x:/g/personal/jason_barnes_usmc-mccs_org/EQ2Kicc4IapDi0aJDUetkCUB4ObLD-WCMv8gLEdScQ2KuQ?e=erfL6q)


Download cleaned Lodging data: [here](https://mccsorg-my.sharepoint.com/:x:/g/personal/jason_barnes_usmc-mccs_org/EX4Vdz_H-7tMkHUU2mg_1A4B_r5IUUc4mTZTyR7GGWHi0Q?e=swZIdx)

DTM 18-007: [here](https://mccsorg-my.sharepoint.com/:b:/g/personal/jason_barnes_usmc-mccs_org/ESdYYeeOBR9HuWwTxLJjh-gBzrxXlDsDBQFhI68WQ-uqRQ?e=ZkQbAr)

SecNav memo: Department of the Navy Lodging Program [here](https://mccsorg-my.sharepoint.com/:b:/g/personal/jason_barnes_usmc-mccs_org/EStws4SskxdBgIVr5HY8P_QBKnTpqAzHhHtUCg_0DJg3cA?e=lyxRwv)

ASN M&RA (Under Secretary) Consolidation of Permanent Change of Station and Temporary Duty Lodging: [here](https://mccsorg-my.sharepoint.com/:b:/g/personal/jason_barnes_usmc-mccs_org/ETpX52-qbX1AqBBg69tYKS8BT1oYcIZAESvO2WxCUE0DaA?e=YRVYUZ)

PDASN Memo to DC, M&RA: [here](https://mccsorg-my.sharepoint.com/:b:/g/personal/jason_barnes_usmc-mccs_org/EYhk3AnPr-5MkWHCCq_llwkBiVyh-EsgD7IH6X_1asJQHA?e=fK5BqR)


</center>

<br>

# Exploring Costs 

---

## Costs by Category

<center>
Facility Sustainment, Restoration and Modernization (FSRM)
</center>

<br>

```{r Category Lodging GT}

category_lodging <- df_lodging %>%
  group_by(naf_cat) %>%
  summarise(
    total_sus = sum(sus),
    total_rm = sum(RM_corrected),
    total = sum(sus) + sum(RM_corrected)
  ) %>%
  arrange(naf_cat) %>%
  gt() %>%
  tab_header(
    title = md("*Annual* MCCS FSRM Costs by Category"),
    subtitle = md("*iNFADS* data retrieved **Sep 28, 2021**")
  ) %>%
  fmt_currency(
    columns = c(total_sus, total_rm, total),
    currency = "USD",
    decimals = 0
  ) %>%
  cols_align(
    align = c("left"),
    columns = everything()
  ) %>%
  tab_footnote(
    footnote = "Lodging NAFI Funding",
    locations = cells_title(groups = "title")
  ) %>%
  tab_footnote(
    footnote = "2.5% of PRV (MCICOM Metric for R&M & New Construction)",
    locations = cells_column_labels(
      columns = total_rm
    )
  ) %>%
  tab_footnote(
    footnote = "Nominal dollars",
    locations = cells_title(groups = "title")
  ) %>%
    grand_summary_rows(
    columns = c(total_sus, total_rm, total),
    fns = list(
      Total = ~ sum(.)
    ),
    missing_text = "FSRM",
    formatter = fmt_currency,
    decimals = 0
  ) %>%
  cols_label(
    naf_cat = "Category",
    total_sus = "Sustainment",
    total_rm = "R & M",
    total = "Total"
  )


category_lodging


```

<br>

---

## Costs by Region

<br>


```{r Region Lodging GT}

region_lodging <- df_lodging %>%
  group_by(region) %>%
  summarise(
    total_sus = sum(sus),
    total_rm = sum(RM_corrected),
    total = sum(sus) + sum(RM_corrected)
  ) %>%
  arrange(desc(total)) %>%
  gt() %>%
  tab_header(
    title = md("*Annual* MCCS FSRM Costs by Region"),
    subtitle = md("**iNFADS* data retrieved **Sep 28, 2021**")
  ) %>%
  fmt_currency(
    columns = c(total_sus, total_rm, total),
    currency = "USD",
    decimals = 0
  ) %>%
  cols_align(
    align = c("left"),
    columns = everything()
  ) %>%
  tab_footnote(
    footnote = "Lodging NAFI Funding",
    locations = cells_title(groups = "title")
  ) %>%
  tab_footnote(
    footnote = "2.5% of PRV (MCICOM Metric for R&M & New Construction)",
    locations = cells_column_labels(
      columns = total_rm
    )
  ) %>%
  tab_footnote(
    footnote = "Nominal dollars",
    locations = cells_title(groups = "title")
  ) %>%
  grand_summary_rows(
    columns = c(total_sus, total_rm, total),
    fns = list(
      Total = ~ sum(.)
    ),
    missing_text = "FSRM",
    formatter = fmt_currency,
    decimals = 0
  ) %>%
  cols_label(
    region = "Region",
    total_sus = "Sustainment",
    total_rm = "R & M",
    total = "Total"
  )

region_lodging

```
